Mental Health Factors and Covid

### 2025-04-20 code/analysis-code/analysis.qmd
Part 5 manuscript updates

# Fit svyglm models for EXERCISE predictor
models_exercise <- lapply(survey_designs, function(dsgn) {
  svyglm(COVID ~ EXERCISE, design = dsgn, family = quasibinomial())
})

# Extract coefficients and standard errors for each model
model_exercise_coef <- lapply(models_exercise, function(model) {
  data.frame(
    Estimate = coef(model),
    Std.Error = sqrt(diag(vcov(model))),
    stringsAsFactors = FALSE
  )
})

# Calculate means and variances for pooling
estimates <- do.call(rbind, lapply(model_exercise_coef, function(x) x$Estimate))
se <- do.call(rbind, lapply(model_exercise_coef, function(x) x$Std.Error))

# Create a data frame with pooled estimates, standard errors, and confidence intervals
pooled_exercise <- data.frame(
  Estimate = mean_estimate,
  Std.Error = pooled_se,
  CI_Low = ci_low,
  CI_High = ci_high
)

# Display the pooled results
pooled_exercise

library(survey)

@@

Now we will make a nice table of that using gt.

@@

#not including intercepts values
# Assuming 'pooled_exercise' is your data frame
pooled_exercise %>%
  group_by(Predictor) %>%
  slice(2) %>%  # Select only the second row for each Predictor
  ungroup() %>%
  mutate(CI = paste0("(", round(CI_Low, 3), ", ", round(CI_High, 3), ")")) %>%
  select(Predictor, OR, CI, p_value) %>%
  gt() %>%
  tab_header(
    title = "Associations of individual mental health factors with positive covid test result"
  ) %>%
  cols_label(
    Predictor = "Predictor",
    OR = "Odds Ratio",
    CI = "Confidence Interval",
    p_value = "P-Value"
  ) %>%
  fmt_number(
    columns = vars(OR, p_value),
    decimals = 3
  )

>>>>

@@

Now we will make a nice table of that using gt and save it to use in the mauscript.

@@

#not including intercepts values
table2 <- pooled_exercise %>%
  group_by(Predictor) %>%
  slice(2) %>%  # Select only the second row for each Predictor
  ungroup() %>%
  mutate(CI = paste0("(", round(CI_Low, 3), ", ", round(CI_High, 3), ")")) %>%
  select(Predictor, OR, CI, p_value) %>%
  gt() %>%
  tab_header(
    title = "Associations of individual mental health factors with positive covid test result"
  ) %>%
  cols_label(
    Predictor = "Predictor",
    OR = "Odds Ratio",
    CI = "Confidence Interval",
    p_value = "P-Value"
  ) %>%
  fmt_number(
    columns = vars(OR, p_value),
    decimals = 3
  )

# Save the table as a PNG
here()
gtsave(table2, here("results", "figures", "single_model_table.png"))

### 2025-04-20 products/manuscript/Manuscript.qmd
Part 5 manuscript updates

```{r}
#| label: fig-schematic
#| fig-cap: "Summary statistics table"
#| echo: FALSE
knitr::include_graphics(here("results","figures", "table1_imputed.png"))
```

```{r}
#| label: tbl-summarytable
#| tbl-cap: "Table. 1. Mental health characteristics among Americans from 2019-2022, by SARS-CoV-2 test result status, NHIS"
#| echo: FALSE
here()
knitr::include_graphics(here("results","figures", "result_table1.png"))
```

@@

_To get some further insight into your data, if reasonable you could compute simple statistics (e.g. simple models with 1 predictor) to look for associations between your outcome(s) and each individual predictor variable. Though note that unless you pre-specified the outcome and main exposure, any "p<0.05 means statistical significance" interpretation is not valid._

fig-result shows a scatterplot figure produced by one of the R scripts.

```{r}
#| label: fig-result
#| fig-cap: "Height and weight stratified by gender."
#| echo: FALSE
#knitr::include_graphics(here("results","figures","height-weight-stratified.png"))
```

>>>>

```{r}
#| label: fig-1
#| fig-cap: "Summary statistics table"
#| echo: FALSE
knitr::include_graphics(here("results","figures", "table1_imputed.png"))
```

@@

```{r}
#| label: tbl-summarytable
#| tbl-cap: "Single model table"
#| echo: FALSE
here()
knitr::include_graphics(here("results","figures", "single_model_table.png"))
```
